Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
Added Bibliography
writing

---
title: Meta-analysis of fungicide application timing for powdery mildew management
  in mungbean.
author: "P. Melloy"
date: "31/01/2020"
output:
  html_document: default
bibliography: Mungbean.bib
---

@@

## Introduction
Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. 
Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43% [@Kelly2017a]. 
Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
### Managements strategies
#### and conditions for infection
Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.

Signs of powdery mildew are almost always first observed when temperatures start to cool.

@@

## Materials and methods

## References

>>>>

---
title: Meta-analysis of fungicide application timing for powdery mildew management
  in mungbean.
author: "P. Melloy"
date: "31/01/2020"
output:
  html_document: default
---

@@

## Introduction
Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. 
Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
However these potenitial crop yields can be limited by powdery mildew (*Podosphaera xanthii*)by up to 40% [@Kelly2017a]. 
Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.

### Managements strategies
#### and conditions for infection
Planting date is an effective way of preventing the development of powdery mildew in mungbean. 
Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.  
Therefore when sowing is delayed there is a greater chance powdery mildew will infect earlier in the crop development leading to greater yield losses.

Commercially available mungbean cultivars in Australia lack suficient resistance to be used soley as a management strategy to avoid yield losses.
Quantitative disease resistance has been shown in a few cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required.

Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease.

@@

*****
## Materials and methods
